---
title: "Test_tommaso_reali"
author: "Tommaso Reali"
format: html
editor: visual
---

## Types and classes

```{r}
typeof(1.5)
typeof("toto")
typeof(TRUE)
typeof(1L)
typeof(typeof)
typeof(list())
```



defines sets with associated operations. R or Z (integer number in mathematics). Types is the computer representation of this. everything is a double except if you . Characters:sequence of letters. Closure is a specific type for functions: don't excpext to be able to sum the functions between them for example. Most of those types have a hardware version on the CPU, It is what is give to you from the programming language There are differenece but we don't care. 


### Classes
classes in Python or R is the way to create your own type. 
```{r}
data(iris)
typeof(iris)
class(iris)
```
## Vectors
Many things in R are vectors (and most of the other things are lists).

A vector is a collection of values of the same type (possibly a single value).

```{r}
x <- 15.25
length(x) ##all vectors have a lenght 
x[1]
typeof(length(x))
length(length(x))
```
## creation function 
c function can be seen as a creation function or, more accurately as a vector concatenation function
```{r}
y <- c(1, -2, 56, 1.7, -1e-10)
y
typeof(y)
y[2]
length(y)
```
## merging vect y and x
```{r}
c(x,y)
```

### Character vectors

This is not R strenght...

```{r}
z <- "Aice Bompard"
length(z)
```

