---
title: "Test_tommaso_reali"
author: "Tommaso Reali"
format: html
editor: visual
---

## Types and classes

```{r}
typeof(1.5)
typeof("toto")
typeof(TRUE)
typeof(1L)
typeof(typeof)
typeof(list())
```



defines sets with associated operations. R or Z (integer number in mathematics). Types is the computer representation of this. everything is a double except if you . Characters:sequence of letters. Closure is a specific type for functions: don't excpext to be able to sum the functions between them for example. Most of those types have a hardware version on the CPU, It is what is give to you from the programming language There are differenece but we don't care. 


### Classes
classes in Python or R is the way to create your own type. 
```{r}
data(iris)
typeof(iris)
class(iris)
```
## Vectors
Many things in R are vectors (and most of the other things are lists).

A vector is a collection of values of the same type (possibly a single value).

```{r}
x <- 15.25
length(x) ##all vectors have a lenght 
x[1]
typeof(length(x))
length(length(x))
```
## creation function 
c function can be seen as a creation function or, more accurately as a vector concatenation function
```{r}
y <- c(1, -2, 56, 1.7, -1e-10)
y
typeof(y)
y[2]
length(y)
```
## merging vect y and x
```{r}
c(x,y)
```

### Character vectors

This is not R strenght...

```{r}
z <- "Aice Bompard (la fille de manuel)"
length(z)
```

Salvation comes from the `string` package.

```{r}
library(stringr)
str_length(z)
```
```{r}
complicated <- "ðŸ˜  à¼ à½–à½€à¾²à¼‹à½¤à½²à½¦à¼‹ à½–à½‘à½ºà¼‹à½£à½ºà½‚à½¦à¼‹à¼" 
complicated
length(complicated)
str_length(complicated)
```
```{r}
some_values <- c("ðŸ˜ ","à½¦à¼‹")
some_values 
length(some_values)
str_length(some_values)
str_to_upper(some_values)
```
```{r}
x <- c(6,5,1,2,3,4)
x[3]
```


```{r}
x[4] <- 15
x
```
Assignment can be understood as a value semantic assignment: `x` and `y` are different vectors with the same intial content

```{r}
y <- x
y
```
Therefore, modifying `x` has no effect on `y`.
```{r}
x[1] <-18
x
y
```

Indexing is made with vectors of any lenght.
```{r}
x
x[c(2,2,1,4,3)]
```
```{r}
x[0] #no way I could understand it 
x[7] #novalue
x[10] #no value
```
```{r}
typeof(numeric(0))
length(numeric(0))
```
```{r}
typeof(NA)
length(NA)
```
```{r}
typeof(NA_integer_)
NA_integer_
```
```{r}
x
x[c(4,1,0,15)]
```
```{r}
c(numeric(0),5,numeric(0))
```
Either all positive or all negative values in the vector
```{r}
x
x[c(-1,-4)]
```


Logical indexing 
```{r}
y <- c("A", "B","C")
y
y[c(TRUE, FALSE,TRUE)]
```
```{r}
x
x[c(1,4)] <- c(-34,42)
x
x[c(2,10)] <- c(123,78)
x
```
```{r}
y <- c("A", "B", "C")
y
y[c(TRUE, FALSE, TRUE)]
```

