---
title: "Resume"
author: "Tony De Amorim"
format: html
---

## Types and classes
### Types

```{r}
typeof(1.5)
typeof("la vida")
typeof('same shit')
typeof(FALSE)
typeof(1L)
typeof(1)
typeof(typeof)
typeof(list())
```

### Classes

```{r}

data(iris)
typeof(iris)
class(iris)

class(1L)

```

Most of the types have a hardware version (not for advanced ones like list). Classes are a way to create types as a developer.  

## Vectors

Collection on values of the same type (possibly a single value)

```{r}

x <- 2.3254
length(x) #all vectors have length

x[1]

# some damn strange things hereby appears

length(length(length(x)))

# bit more developed

y <- c(1,3.8,4.8888888, 9.0)
length(y)
typeof(y)
class(y)
y[3]
```

Can think of c() as a creation / vector concatenation function. 

# Stringr package

```{r}
#having an issue there :

n <- "Luigi"
length(n)

#this package is our lord and savior
library(stringr)

str_length(n)

# other thing

s <- "😉😂😊😋😃😋"
s
length(s)
str_length(s)

```

Everything is a vector, reminding that helps understanding every bullshit things R might do. 
