---
title: "Resume"
author: "Tony De Amorim"
format: html
---

## Types and classes
### Types

```{r}
typeof(1.5)
typeof("la vida")
typeof('same shit')
typeof(FALSE)
typeof(1L)
typeof(1)
typeof(typeof)
typeof(list())
```

### Classes

```{r}

data(iris)
typeof(iris)
class(iris)

class(1L)

```

Most of the types have a hardware version (not for advanced ones like list). Classes are a way to create types as a developer.  

## Vectors

Collection on values of the same type (possibly a single value)

```{r}

x <- 2.3254
length(x) #all vectors have length

x[1]

# some damn strange things hereby appears

length(length(length(x)))

# bit more developed

y <- c(1,3.8,4.8888888, 9.0)
length(y)
typeof(y)
class(y)
y[3]
```

Can think of c() as a creation / vector concatenation function. 

# Stringr package

```{r}
#having an issue there :

n <- "Luigi"
length(n)

#this package is our lord and savior
library(stringr)

str_length(n)

# other thing

s <- "😉😂😊😋😃😋"
s
length(s)
str_length(s)

```

Everything is a vector, reminding that helps understanding every bullshit things R might do. 


## Indexing

Used to modify objects

```{r}
x <- c(1,2,3,4578)

x[2] <- x[4] - 4570

x
```

x is not y duh

```{r}
y <- x

x[3] <- 0

y 
x
```

Modifying x has no effect on y. y is a "lazy copy" : y is initialy x but whenever I modify y it creates a copy

Wattabout indexing by a vector ?

```{r}

x
x[c(2,2,1,4,3)] # displaying some values multiple times

# and if I do that ?

x[0] # gives an empty vector
x[7] # gives NA

# Thus

x[c(1,2,0,8)]

c(numeric(0), 5, numeric(0))

x[c(-1,-3)]

# Other possibilities

x[c(1,4)] <- c(2200,2202)
x
x[c(5,9)] <- c(2208,2222999)
x

```


Logical indexing 


```{r}

hidalgo <- c("Maire", "De", "Paris")
hidalgo
hidalgo[c(TRUE,FALSE,TRUE)]

```




